J-Study manuscript

### 2023-05-18 writing/ms.Rmd
add loose stats for model fact by both

coefs_fact_by_source <- tar_read(preplot_params_fact_by_source, store = target_store) %>%
  summarize_report(col = estimate, term, stat_name = "beta")
```

@@

>>>>

coefs_fact_by_source <- tar_read(preplot_params_fact_by_source, store = target_store) %>%
  summarize_report(col = estimate, term, stat_name = "beta")

coefs_fact_by_both <- tar_read(preplot_params_fact_by_both, store = target_store) %>%
  summarize_report(col = estimate, term, stat_name = "beta")
```

@@

```{r}
preplot_fixef_fact_by_both <- tar_read(preplot_fixef_fact_by_both, store = target_store)

preplot_fixef_fact_by_both %>% 
  mutate(across(c(j_score, resp_pic, resp_source), \(x) if_else(x > 0, "high", "low")),
         resp_pic = paste0("pic.", resp_pic),
         resp_source = paste0("source.", resp_source)) %>% 
  pivot_wider(names_from = c(resp_pic, resp_source),
              values_from = acc_pred) %>% 
  mutate(superdiff = (pic.high_source.high - pic.low_source.high) - (pic.high_source.low - pic.low_source.low)) %>% 
  select(-starts_with("pic.")) %>% 
  group_by(j_score) %>% 
  summarize(avg = mean(superdiff, na.rm = T),
            q025 = quantile(superdiff, .025, na.rm = T),
            q500 = median(superdiff, na.rm = T),
            q975 = quantile(superdiff, .975, na.rm = T))
```
